Quantum Walks and Applications to Quantum Money

### 2025-04-02 presentation.tex
presentation updated

        \[
        \ket{\phi_{j0}} := \frac{1}{\sqrt{d}}\sum_{l \in F_j}(\sqrt{\frac{H^*_{jl}}{K}}\ket{0} + \sqrt{1-\frac{|H^*_{jl}|}{K}}\ket{1})
        \]

        \[
        \ket{\phi_{j1}} := \ket{0}\ket{1} 
        \]

        \[
        T := \sum_{j=0}^{N-1}\sum_{b \in {\{0,1\}}}(\ket{j}\bra{j}\otimes\ket{b}\bra{b})\otimes\ket{\phi_{jb}}
        \]

        \[
        W = iS(2TT^* - 1)
        \]

        \[
        S\ket{j_1,b_1}\ket{j_2,b_2} = \ket{j_2,b_2}\ket{j_1,b_1}
        \]

@@

       \[
       e^{-iAt} = \operatorname{QFT_G}(\sum_{a \in G}e^{-i\lambda_at}\ket{a}\bra{a})\operatorname{QFT^*_G}
       \]

% \begin{frame}{Simulating group action quantum walks}

@@

%         \[
%         e^{-iAt} = \sum_{h \in G}\ket{G^{(h)}*x}\bra{G^{(h)}*x}
%         \]

%         \[
%         T := \sum_{y \in X}\sum_{b \in {\{0,1\}}}(\ket{j}\bra{j}\otimes\ket{b}\bra{b})\otimes\ket{\phi_{yb}}
%         \]

%         \[
%         = \sum_{y \in X}\sum_{b \in {\{0,1\}}}\ket{y}\ket{b}\ket{\phi_{yb}}\bra{y}\bra{b}
%         \]

%         \[
%             \ket{\phi_{y0}} = \frac{1}{\sqrt{|Q|}}\sum_{q \in Q}\ket{q*y}\ket{0}
%         \]

@@

>>>>

    \textbf{Abelian Groups:}
    \begin{itemize}
        \item $e^{-iAt} = \text{QFT}_G \left( \sum_{a \in G} e^{-i\lambda_a t} |a\rangle\langle a| \right) \text{QFT}_G^*$
        \item Efficient since:
        \begin{itemize}
            \item QFT$_G$ and QFT$_G^*$ run in poly$(\log|G|)$ time.
            \item $\lambda_a$ computable to high precision classically.
        \end{itemize}
    \end{itemize}

    \vspace{0.5cm}
    \textbf{Group Actions:}
    \begin{itemize}
        \item No efficient QFT-like decomposition.
        \item Can express:
        \[
        e^{-iAt} = \sum_{h \in G} e^{-i\lambda_h t} |G^{(h)} * x\rangle\langle G^{(h)} * x|
        \]
        \item But still approximable for $t = \text{poly}(\log|G|)$ due to structure in $A$.
    \end{itemize}

@@

% \begin{frame}{Simulating continuous-time walks}

@@

%         \[
%         \ket{\phi_{j0}} := \frac{1}{\sqrt{d}}\sum_{l \in F_j}(\sqrt{\frac{H^*_{jl}}{K}}\ket{0} + \sqrt{1-\frac{|H^*_{jl}|}{K}}\ket{1})
%         \]

%         \[
%         \ket{\phi_{j1}} := \ket{0}\ket{1} 
%         \]

%         \[
%         T := \sum_{j=0}^{N-1}\sum_{b \in {\{0,1\}}}(\ket{j}\bra{j}\otimes\ket{b}\bra{b})\otimes\ket{\phi_{jb}}
%         \]

%         \[
%         W = iS(2TT^* - 1)
%         \]

%         \[
%         S\ket{j_1,b_1}\ket{j_2,b_2} = \ket{j_2,b_2}\ket{j_1,b_1}
%         \]

@@

        \textbf{Goal:} Efficiently simulate $W = e^{-iAt}$ for $t = \text{poly}(\log |G|)$.

        \medskip
        \textbf{Approach:} Use discrete-time quantum walk framework:
        \[
        W = iS(2TT^* - 1)
        \]

        \begin{itemize}
        \item Isometry $T$ and its adjoint $T^*$ are efficiently implemented via simple unitaries $U_0$, $U_1$.
        \item These unitaries prepare/refactor states $|\varphi_{yb}\rangle$ using a small symmetric set $Q \subset G$.
        \item Efficient due to:
            \begin{itemize}
            \item Bounded degree Cayley graph.
            \item Polynomial-size $Q$ allows brute-force mapping.
            \end{itemize}
        \item Full walk operator $W$ simulated via reflection trick using $T$, $T^*$, and ancilla control.
        \end{itemize}

        \textbf{Conclusion:} Group-action quantum walks can be simulated efficiently despite lack of QFT-like structure.
